### 2015-05-12 whoop.tex
updates to SMACK text

To achieve scalability, SMACK is using a split-memory model instead of a monolithic one that would be difficult for backend verifiers to reason about~\cite{rakamaric2009scalable}. This split memory model is based on \emph{memory regions}, which are maps of integers that model the heap. A benefit of using this model is that memory regions denote disjoint sections of the heap (i.e. pointers that cannot alias). We leverage this knowledge inside \whoop to guide and optimize our instrumentation and analysis. In reality, this memory model is unsound ... (e.g. integers, overflow?), but for our work we assume it is sound.

>>>>

To achieve scalability, SMACK is using a split-memory model instead of a monolithic one that would be difficult for backend verifiers to reason about~\cite{rakamaric2009scalable}. This split memory model is based on \emph{memory regions}, which are maps of integers that model the heap. A benefit of using this model is that memory regions denote disjoint sections of the heap (i.e. pointers that cannot alias). We leverage this knowledge inside \whoop to guide and optimize our lockset instrumentation and analysis, and to create a fine-grained granularity of context-switch instrumentation as discussed in Section~\ref{corral}.

In reality, SMACK is unsound ... (e.g. integers), but for our work we assume it is sound.
